---
title: "FirstMarkdown"
author: "Alexander Kissonergis"
date: "2024-01-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#we can use LaTeX to create proper looking equations and. greek symbols using two $ operators on either side of the equation, see notes in the online lecture series, specifically the Markdown lectures. EX: $$xxxxxxx$$


#Sometimes we want to mix the mathematical symbols with plain text font, to do this in LaTeX we must use a structure called "mbox" to keep the string separate from being considered a variable. 

#you can embed LaTeX in line $\pi + 3$ as such
#we can also use markdown fencing in line with a single backtick `pi + 3`
#see notes for the difference in the above two, the second does not show the greek symbol for pi

#we can even execute r code inside of markdown text with `r pi + 3` this will return the output of pi + 3


```{r} 
#this creates an r chunk 

Pred <- seq(1,10)  #make a vector of integers from 1 to 10
Res <- runif(10)   #generate 10 draws from a random uniform (0,1) distribution

#print the random numbers
print(Res)


