---
title: "Homework_6"
author: "Alexander Kissonergis"
date: "2024-03-01"
output: html_document
---
The data I used for this assignment I pulled from dryad:
Coverdale, Tyler; Agrawal, Anurag (2022). Data from: Experimental insect suppression causes loss of induced, but not constitutive, resistance in Solanum carolinense [Dataset]. Dryad.

Following the code given in the first part of the homework:
```{r}
library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

# quick and dirty, a truncated normal distribution to work on the solution set

y <- rnorm(n=3000,mean=0.2)
y <- data.frame(1:3000,y)
names(y) <- list("ID","myVar")
y <- y[y$myVar>0,]
str(y)
summary(y$myVar)

#plotting histogram of data
p1test <- ggplot(data=y, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1test)

#adding empirical density curve
p1test <-  p1test +  geom_density(linetype="dotted",size=0.75)
print(p1test)

#getting maximum likelihood parameters for normal
normPars <- fitdistr(z$myVar,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute

#plotting normal probability density
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$myVar),len=length(z$myVar))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$myVar), args = list(mean = meanML, sd = sdML))
 p1 + stat
 
#plotting exponential probability density
expoPars <- fitdistr(z$myVar,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$myVar), args = list(rate=rateML))
 p1 + stat + stat2 
 
#plotting uniform probability density
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$myVar), args = list(min=min(z$myVar), max=max(z$myVar)))
 p1 + stat + stat2 + stat3
 
#plotting gamma probability density
gammaPars <- fitdistr(z$myVar,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$myVar), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
 
#plotting beta probability density
pSpecial <- ggplot(data=z, aes(x=myVar/(max(myVar + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$myVar/max(z$myVar + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$myVar), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
 
```

And with data from dryad 
```{r}
z <- read.csv("Supplemental_Data_2.csv",header=TRUE,sep=",")
str(z)
summary(z)

p1 <- ggplot(data = z, aes(x = Mean.height..cm.)) +
geom_histogram(aes(fill = Mean...prickles), color = "grey60", bins = 30) +
scale_fill_gradient(low = "cornsilk", high = "cornflowerblue") + # Gradient fill color
labs(x = "Mean Height (cm)", y = "Frequency") 
print(p1)

#plotting histogram of data
p1 <- ggplot(data = z, aes(x = Mean.height..cm.)) +
geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)

#adding empirical density curve
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)

#getting maximum likelihood parameters for normal
normPars <- fitdistr(z$Mean.height..cm.,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute

#plotting normal probability density
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$Mean.height..cm.),len=length(z$Mean.height..cm.))

stat <- stat_function(aes(x = xval, y = Mean.height..cm.), fun = dnorm, colour="red", n = length(z$Mean.height..cm.), args = list(mean = meanML, sd = sdML))
p1 + stat
 
#plotting exponential probability density
expoPars <- fitdistr(z$Mean.height..cm.,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = Mean.height..cm.), fun = dexp, colour="blue", n = length(z$Mean.height..cm.), args = list(rate=rateML))
p1 + stat + stat2 
 
#plotting uniform probability density
stat3 <- stat_function(aes(x = xval, y = Mean.height..cm.), fun = dunif, colour="darkgreen", n = length(z$Mean.height..cm.), args = list(min=min(z$Mean.height..cm.), max=max(z$Mean.height..cm.)))
p1 + stat + stat2 + stat3
 
#plotting gamma probability density
gammaPars <- fitdistr(z$Mean.height..cm.,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = Mean.height..cm.), fun = dgamma, colour="purple", n = length(z$Mean.height..cm.), args = list(shape=shapeML, rate=rateML))
p1 + stat + stat2 + stat3 + stat4 

#plotting beta probability density
pSpecial <- ggplot(data=z, aes(x=Mean.height..cm./(max(Mean.height..cm. + 0.1)), y=Mean.height..cm.)) +
geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
xlim(c(0,1)) +
geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$Mean.height..cm./max(z$Mean.height..cm. + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = Mean.height..cm.), fun = dbeta, colour="orchid", n = length(z$Mean.height..cm.), args = list(shape1=shape1ML,shape2=shape2ML))
#pSpecial + statSpecial
 
```

The normal distribution looks like it fits the best, so I will go with that one. 

Mean = 26.4
SD = 4.05

Now creating another data set with the parameters from the normal distribution. 

```{r}
y <- rnorm(n=15,mean=26.4,sd=4.05)
y <- data.frame(1:15,y)
names(y) <- list("ID","myVar")
y <- y[y$myVar>0,]
str(y)
summary(y$myVar)

#plotting histogram of data
p1normal <- ggplot(data=y, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1normal)

#adding empirical density curve
p1normal <-  p1normal +  geom_density(linetype="dotted",size=0.75)
print(p1normal)

#getting maximum likelihood parameters for normal
normPars <- fitdistr(y$myVar,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute

#plotting normal probability density
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(y$myVar),len=length(y$myVar))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(y$myVar), args = list(mean = meanML, sd = sdML))
 p1 + stat
 
```

The histogram profiles appear to be similar. I do think that in the future I will use a larger data set. Part of the problem with my lack of comfort with the results is the lack of data, there are very few data points, something I didn't think about much when I pulled the data. This makes me unsure about the entire thing. 