---
title: "Homework_5"
author: "Alexander Kissonergis"
date: "2024-02-14"
output: html_document
---

1) Assign to the variable n_dims a single random integer between 3 and 10.

- Create a vector of consecutive integers from 1 to n_dims squared

- Use the sample function to randomly reshuffle these values.

- Create a square matrix with these elements.

- Print out the matrix.

- Find a function in r to transpose the matrix.

- Print it out again and note how it has changed.

- Calculate the sum and the mean of the elements in the first row and then the last row.

- Read about the eigen() function and use it on your matrix

- Look carefully at the elements of values and vectors in the output. What kind of numbers are these?

- Dig in with the typeof() function to figure out their type.

- If have set your code up properly, you should be able to re-run it and create a matrix of different size because n_dims will change.

```{r}

n_dims <- sample(3:10, 1)

vector <- c(1:n_dims^2)

vector

shuffled_vector <- sample(vector)

square_matrix <- matrix(data = shuffled_vector, nrow = n_dims^2, ncol = n_dims^2)

print(square_matrix)

t(square_matrix)

print(square_matrix)

sum(square_matrix[1,])

sum(square_matrix[36,])

eigen_square_matrix <- eigen(square_matrix)

#the values and vectors both seem to be imaginary numbers

typeof(eigen_square_matrix$values)
typeof(eigen_square_matrix$vectors)

#this is confirmed by checking the type of for both 
```

Create a list with the following named elements:

- my_matrix, which is a 4 x 4 matrix filled with random uniform values
- my_logical which is a 100-element vector of TRUE or FALSE values. Do this efficiently by setting up a vector of random values and then applying an inequality to it.
- my_letters, which is a 26-element vector of all the lower-case letters in random order.

Then, complete the following steps:

- Create a new list, which has the element[2,2] from the matrix, the second element of the logical vector, and the second element of the letters vector.

- Use the typeof() function to confirm the underlying data types of each component in this list

- Combine the underlying elements from the new list into a single atomic vector with the c() function.
- What is the data type of this vector?
```{r}
#creating my_matrix per instructions
my_matrix <- matrix(runif(16), nrow = 4)
my_matrix

#creating my_logical per instructions
my_logical <- runif(100) > .5
my_logical 

#creating my_letters per instructions
my_letters <- sample(letters, 26)
my_letters

#creating my_list per instructions
my_list <- list( my_matrix[2,2],my_logical[2],my_letters[2])
my_list

#checking element type
typeof(my_list[[1]]) #double
typeof(my_list[[2]]) #logical
typeof(my_list[[3]]) #character

my_atomic_vector <- c(my_matrix[2,2],my_logical[2],my_letters[2])

typeof(my_atomic_vector[1:3])

#it is of type: character
```
Create a data frame with the two variables (= columns) and 26 cases (= rows) below:

- Call the first variable my_unis and fill it with 26 random uniform values from 0 to 10

- Call the second variable my_letters and fill it with 26 capital letters in random order.

- For the first variable, use a single line of code in R to select 4 random rows and replace the numerical values in those rows with NA.

- For the first variable, write a single line of R code to identify which rows have the missing values.

- Re-order the entire data frame to arrange the second variable in alphabetical order

- Calculate the column mean for the first variable.

```{r}
#creating my_unis per instruction
my_unis <- runif(26, min=0, max=10)

#creating my_letters per instruction
my_letters <- sample(LETTERS)
my_letters

#creating df, then selecting 4 random rows and replacing the numerical values in those rows with NA
my_dataframe <- data.frame(my_unis, my_letters)

my_dataframe[sample(my_unis, 4), 1] <- NA

#identifying missing values

which(is.na(my_dataframe$my_unis))
#4,5,6,8 are missing values, which shows as true upon checking, I used is.na as I prefer it from previous experience in python

#re-ordering dataframe per instruction
reordered_dataframe <- my_dataframe[order(my_dataframe$my_letters), ]

#calculating mean, need to remove NA's to calculate
mean(my_dataframe$my_unis, na.rm = TRUE)
```