---
title: "Homework_7"
author: "Alexander Kissonergis"
date: "2024-03-06"
output: html_document
---
Here I will be creating a data set that might mimic the hormetic effects we see after an insect has had exposure to pesticide. We should see a dramatic difference in cell count response, with the treatment showing a higher cell count. The numbers are highly dependent on the methods used, so in this case, I am using numbers that are arbitrarily matching patterns.

```{r}
#loading in ggplot
library(ggplot2)

#setting a seed for reproducible data
set.seed(190)

# creating my treatment groups, here I am using SD to define the range instead of what we did in class
control <- rnorm(100, mean = 25000, sd = 1000)
treated <- rnorm(100, mean = 30000, sd = 1000)

# Create sample IDs
sample_ids <- paste(1:200)

#  creating a dataframe named z in the spirit of continuing the classes methods, I am using a
z <- data.frame(
  Sample_ID = sample_ids,
  Group = rep(c("Control", "Treated"), each = 100),
  Cell_Count = c(control, treated)
)

# the creation of the histogram from last class is a bit confusing so using this method from ggplot instead
OG_plot <- ggplot(z, aes(x = Cell_Count, fill = Group)) +
  geom_histogram(binwidth = 500, position = "dodge", color = "black") +
  labs(title = "Histogram of Cell Count by Treatment Group",
       x = "Cell Count", y = "Frequency") +
  scale_fill_manual(values = c("Control" = "blue", "Treated" = "red")) +
  theme_minimal()

print(OG_plot)

#adding a geom den curve, however, this doesn't seem to be following the trend, perhaps since the two treatments are so different?

OG_plot <-  OG_plot +  geom_density(linetype="dotted",size=0.75)
print(OG_plot)

```

Since I am just trying to compare the mean cell counts between the two treatments, I will use an ANOVA

```{r}
#running an anova

anova <- aov(Cell_Count ~ Group, data = z)
summary(anova)

```
Testing out different means and retesting anova
```{r}
#testing out different means

#setting a seed for reproducible data
set.seed(190)

# creating my treatment groups, here I am using SD to define the range instead of what we did in class
control <- rnorm(100, mean = 25000, sd = 1000)
treated <- rnorm(100, mean = 27000, sd = 1000)

# Create sample IDs
sample_ids <- paste(1:200)

#  creating a dataframe named z in the spirit of continuing the classes methods, I am using a
z2 <- data.frame(
  Sample_ID = sample_ids,
  Group = rep(c("Control", "Treated"), each = 100),
  Cell_Count = c(control, treated)
)

# the creation of the histogram from last class is a bit confusing so using this method from ggplot instead
OG_plot2 <- ggplot(z2, aes(x = Cell_Count, fill = Group)) +
  geom_histogram(binwidth = 500, position = "dodge", color = "black") +
  labs(title = "Histogram of Cell Count by Treatment Group",
       x = "Cell Count", y = "Frequency") +
  scale_fill_manual(values = c("Control" = "blue", "Treated" = "red")) +
  theme_minimal()

print(OG_plot2)

anova2 <- aov(Cell_Count ~ Group, data = z2)

```

Ok, we STILL aren't close, I am going to make the means even closer since we are still getting a very (near 0) significant result

```{r}
#setting a seed for reproducible data
set.seed(190)

# creating my treatment groups, here I am using SD to define the range instead of what we did in class
control <- rnorm(100, mean = 25000, sd = 1000)
treated <- rnorm(100, mean = 25555, sd = 1000)

# Create sample IDs
sample_ids <- paste(1:200)

#  creating a dataframe named z in the spirit of continuing the classes methods, I am using a
z3 <- data.frame(
  Sample_ID = sample_ids,
  Group = rep(c("Control", "Treated"), each = 100),
  Cell_Count = c(control, treated)
)

# the creation of the histogram from last class is a bit confusing so using this method from ggplot instead
OG_plot3 <- ggplot(z3, aes(x = Cell_Count, fill = Group)) +
  geom_histogram(binwidth = 500, position = "dodge", color = "black") +
  labs(title = "Histogram of Cell Count by Treatment Group",
       x = "Cell Count", y = "Frequency") +
  scale_fill_manual(values = c("Control" = "blue", "Treated" = "red")) +
  theme_minimal()

print(OG_plot3)

anova3 <- aov(Cell_Count ~ Group, data = z3)
summary(anova3)
```
It's STILL significant, and hasn't changed in the degree. I will try again. Ok, the results are no longer significant, I will move back upwards in the mean. 
```{r}
#setting a seed for reproducible data
set.seed(190)

# creating my treatment groups, here I am using SD to define the range instead of what we did in class
control <- rnorm(100, mean = 25000, sd = 1000)
treated <- rnorm(100, mean = 25250, sd = 1000)

# Create sample IDs
sample_ids <- paste(1:200)

#  creating a dataframe named z in the spirit of continuing the classes methods, I am using a
z4 <- data.frame(
  Sample_ID = sample_ids,
  Group = rep(c("Control", "Treated"), each = 100),
  Cell_Count = c(control, treated)
)

# the creation of the histogram from last class is a bit confusing so using this method from ggplot instead
OG_plot4 <- ggplot(z4, aes(x = Cell_Count, fill = Group)) +
  geom_histogram(binwidth = 500, position = "dodge", color = "black") +
  labs(title = "Histogram of Cell Count by Treatment Group",
       x = "Cell Count", y = "Frequency") +
  scale_fill_manual(values = c("Control" = "blue", "Treated" = "red")) +
  theme_minimal()

print(OG_plot4)

anova4 <- aov(Cell_Count ~ Group, data = z4)
summary(anova4)
```

It looks like right around 25450 (probably a bit before) is where we start to get a significant difference (one asterisk on the output, p = 0.0108 *). So it seems we can get around a mean difference of 450 cells for the effects size. 
```{r}
#setting a seed for reproducible data
set.seed(190)

# creating my treatment groups, here I am using SD to define the range instead of what we did in class
control <- rnorm(100, mean = 25000, sd = 1000)
treated <- rnorm(100, mean = 25450, sd = 1000)

# Create sample IDs
sample_ids <- paste(1:200)

#  creating a dataframe named z in the spirit of continuing the classes methods, I am using a
z5 <- data.frame(
  Sample_ID = sample_ids,
  Group = rep(c("Control", "Treated"), each = 100),
  Cell_Count = c(control, treated)
)

# the creation of the histogram from last class is a bit confusing so using this method from ggplot instead
OG_plot5 <- ggplot(z5, aes(x = Cell_Count, fill = Group)) +
  geom_histogram(binwidth = 500, position = "dodge", color = "black") +
  labs(title = "Histogram of Cell Count by Treatment Group",
       x = "Cell Count", y = "Frequency") +
  scale_fill_manual(values = c("Control" = "blue", "Treated" = "red")) +
  theme_minimal()

print(OG_plot5)

anova5 <- aov(Cell_Count ~ Group, data = z5)
summary(anova5)
```

ok now I will be getting rid of the seed just to test for a bit of random variation per the hw instructions. These results were extremely significant. Much different result than the last time. 
```{r}

# creating my treatment groups, here I am using SD to define the range instead of what we did in class
control <- rnorm(100, mean = 25000, sd = 1000)
treated <- rnorm(100, mean = 25450, sd = 1000)

# Create sample IDs
sample_ids <- paste(1:200)

#  creating a dataframe named z in the spirit of continuing the classes methods, I am using a
zRANDOM <- data.frame(
  Sample_ID = sample_ids,
  Group = rep(c("Control", "Treated"), each = 100),
  Cell_Count = c(control, treated)
)

# the creation of the histogram from last class is a bit confusing so using this method from ggplot instead
OG_plot_RANDOM <- ggplot(zRANDOM, aes(x = Cell_Count, fill = Group)) +
  geom_histogram(binwidth = 500, position = "dodge", color = "black") +
  labs(title = "Histogram of Cell Count by Treatment Group",
       x = "Cell Count", y = "Frequency") +
  scale_fill_manual(values = c("Control" = "blue", "Treated" = "red")) +
  theme_minimal()

print(OG_plot_RANDOM)

anova_RANDOM <- aov(Cell_Count ~ Group, data = zRANDOM)
summary(anova_RANDOM)
```

Trying again. And again very significant. It seems there is a wide variety of potential effect size. Running it a third time and the result was no longer significant. A fourth times showed no significance as well. A fifth time was very significant.

```{r}

# creating my treatment groups, here I am using SD to define the range instead of what we did in class
control <- rnorm(100, mean = 25000, sd = 1000)
treated <- rnorm(100, mean = 25450, sd = 1000)

# Create sample IDs
sample_ids <- paste(1:200)

#  creating a dataframe named z in the spirit of continuing the classes methods, I am using a
zRANDOM <- data.frame(
  Sample_ID = sample_ids,
  Group = rep(c("Control", "Treated"), each = 100),
  Cell_Count = c(control, treated)
)

# the creation of the histogram from last class is a bit confusing so using this method from ggplot instead
OG_plot_RANDOM <- ggplot(zRANDOM, aes(x = Cell_Count, fill = Group)) +
  geom_histogram(binwidth = 500, position = "dodge", color = "black") +
  labs(title = "Histogram of Cell Count by Treatment Group",
       x = "Cell Count", y = "Frequency") +
  scale_fill_manual(values = c("Control" = "blue", "Treated" = "red")) +
  theme_minimal()

print(OG_plot_RANDOM)

anova_RANDOM <- aov(Cell_Count ~ Group, data = zRANDOM)
summary(anova_RANDOM)
```

